---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CoV

This is my first repository on GitHub!

This repository specifically contains the metadata for my own package called 'CoV'.

## Package Description

The 'CoV' package calculates the coefficient of variance of a specific variable/column. It calculates the CoV by first calculating the standard deviation and mean using sd() and mean(), then multiplying the value by 100

## Installation

You will first need to install and load the following packages
``` r
install.packages("devtools")
library(devtools)
install.packages("testthat")
library(testthat)
install.packages("roxygen2")
library(roxygen2)
```

You can install the released version of CoV from GitHub with:

``` r
install_github("sr2480/CoV")
load_all()
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(CoV)

CoV(c(-200:-1, NA))

CoV(sample(x=1:1000, size=20))
```


