---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CoV

This is my first repository on GitHub!

This repository specifically contains the metadata for my own package called 'CoV'.

## Package Description

The 'CoV' package calculates the coefficient of variance of a specific variable/column. It calculates the CoV by first calculating the standard deviation and mean using sd() and mean(), then multiplying the value by 100

## Installation

You will first need to install and load the following packages
``` r
install.packages("devtools")
library(devtools)
install.packages("testthat")
library(testthat)
install.packages("roxygen2")
library(roxygen2)
```

You can install the released version of CoV from GitHub with:

``` r
install_github("sr2480/CoV")
load_all()
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(CoV)

CoV(c(-200:-1, NA))

CoV(sample(x=1:1000, size=20))
```

# Steps for Creating this Package

## Initialize a new package in a directory

Create the path for where the package goes on your computer! **Run this code in the console** All devtool functions should be run in the console!

create_tidy_package(INSERT_PATH_TO_PACKAGE)

## Version control- Make your R package a GitHub repository in the console! Then restart RStudio!

First type --> git init https://github.com/sr2480/CoV.git in the **terminal**

## Check that you did indeed initialize a github repository by using this code:

dir_info(all = TRUE, regexp = "^[.]git$") %>% 
  select(path, type)
  
**then** 

to make commits use --> use_git() in the **terminal**

## Making .R files for your function!

Every time you make a function a new .R file must be made and you call the file the name of your function...

use_r(“CoV”)

## Creating a Roxygen in your .R function file

Click anywhere within the function in your .R file and click the 'Code' tab then 'Insert Roxygen Skeleton'

•	Input text for ‘param’, ‘return’, ‘export’ and ‘examples’!
•	NOTE: Anytime you change the roxygen you need to run document()

## Call load_all() to make CoV() available for experimentation!

load_all()

## Check that your R package is in working order!

check()

## Editing the DESCRIPTION file

This file provides metadata about your package (Make yourself the author and write some descriptive text in the ‘Title’ and ‘Description’ fields).

## Testing the Function

To test your work from RStudio use:
use_testthat()

To test your work from the console use:
test()

## Adding dependencies

There are three types of dependencies: Suggests, Imports, or Depends.

You can change the type by using the argument ‘type='

use_package(“insert_package”)
use_package("insert_package", type = "depends")

## Adding Vignettes

Vignettes are like a tutorial for a function.

use_vignette(“insert_function”)

OR

build_vignette(“insert_function”)







